Tsbrowse: a genome browser for Ancestral Recombination Graphs

### 2025-03-27 manuscript/paper.tex

\section*{Acknowledgments}
\section*{Author contributions}
\section*{Supplementary Data}
Supplementary data are available at \textcolor{red}{Bioinformatics online}.
\section*{Conflict of interest}
No competing interest is declared.
\section*{Funding}
This work was supported by funding from the Biotechnology and Biological
Sciences Research Council (UKRI-BBSRC) [grant number BB/T008784/1],
\textcolor{red}{add Novo funding and funding details for Ben, Duncan, Jerome}.
\bibliographystyle{natbib}
\bibliography{reference}

>>>>

% \section*{Acknowledgments}
% \section*{Author contributions}
% \section*{Supplementary Data}
% Supplementary data are available at \textcolor{red}{Bioinformatics online}.
% \section*{Conflict of interest}
% No competing interest is declared.

\section*{Funding}
This work was supported by funding from the Biotechnology and Biological
Sciences Research Council (UKRI-BBSRC) [grant number BB/T008784/1],
\textcolor{red}{add Novo funding and funding details for Duncan}.
JK acknowledges EPSRC (research grant EP/X024881/1),
NIH (research grants HG011395 and HG012473)
and the Robertson Foundation.

\bibliographystyle{natbib}
\bibliography{reference}
